A Switching Planner for Combined Task and Observation Planning

### 2010-11-30 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
minor corrections

  \subfloat[Remove facts that are not part of an assumption.]{

@@

  \subfloat[Re-add relevant facts until the belief space limit is reached.]{

@@

In the first step, we remove all facts that are not part of an
assumption (Fig. \ref{fig:abstraction-b}). At this point, the session
would proceed in an abstraction of the environment where that does not
contain $\pp{place2}$, the $\pp{cup}$ or a $\pp{kitchen}$.

>>>>

  \subfloat[Removing facts that are not part of an assumption.]{

@@

  \subfloat[Re-adding relevant facts until the belief-state size limit is reached.]{

@@

In the first step, we remove all facts that are not part of an
assumption (Fig. \ref{fig:abstraction-b}). At this point, the session
would proceed in an abstraction of the environment that does not
contain $\pp{place1}$, the $\pp{cup}$ or a $\pp{kitchen}$.
